Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-06 Latex/tex/pr.tex
comlete part of latex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

Suppose that there are $S$ Slices Serving $V$ Services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs. All the RRHs in a slice that is mapped to a service, transmit signals to all the UEs in specific service. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity. Also each RRH and PRB can serve more than one slice. It is considered that in BBU, the system has 2 processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.

@@

Suppose that we have two processing layer in BBU of O-RAN system. As it is mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer. Each VM in both layers map to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer. Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. \\

@@

&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 
&D_{s} \leq D_{s}^{th}  &&\quad \forall s, \\

@@

@@

&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{max} && \quad \forall v, \forall k, \\                                 

@@

\subsection{Proposed Method}

@@

@@

In this part, we want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
two different part that iteratively solve. 
Firstly, we want to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1}. This part of problem is solved in two different method. The first method is using MOSEK and second method is a heuristic method.

@@

\State Sort Services according to their priority and the number of Users in the services and their requirements.
\State Sort Slices according to the number of PRBs and number of RRHs and VMs  and their max of Capacities of resources. 
\State Set the maximum number of iterations $I_{max}$
\For {$ 1\leq i \leq  Imax$}
\State Solve the resource allocation problem with $\eta^{(i)}$ (Inner Loop);
\State Obtain $P^{(i)}, R_{total}^{(i)}, P_{RRH}^{(i)}$
\If {$ R_{total}(\boldsymbol{P}^{(i)}) - \eta^{(i)} P_{RRH}(\boldsymbol{P}^{(i)}) < \epsilon_{\eta} $} 
\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
\State break;

@@

\State Set $\eta^{(i)}= \frac{R_{total}(\boldsymbol{P}^{(i))}}{P_{RRH}(\boldsymbol{P}^{(i))}}$ and $i= i+1$;

@@

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

Suppose that there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna users that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $N_s$ PRBs. All the RRHs in a slice that is mapped to a service, transmit signals to all the UEs in specific service. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity. Also each RRH and PRB can serve more than one slice. It is considered that in BBU, the system has two processing layer consists of $M_1$ homogeneous VMs in first layer and $M_2$ homogeneous VMs in second layer.

@@

Suppose that we have two processing layer in BBU of O-RAN system. The lower layer is consist of PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.\newline   
As it is mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer. Each VM in both layers map to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer. Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. \\

@@

\text{subject to} \quad  & \bar{p}_{r_{(s,i)}} \leq P_{max} && \quad \forall s, \forall i, 
 \label{c11} \\
&p_{u_{(v,k)}}  \geq 0  &&\quad \forall v, \forall k,\label{c12} \\
&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k,\label{c13} \\                                 
&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \label{c14}\\
&D_{s} \leq D_{s}^{th}  &&\quad \forall s,\label{c15} \\
& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \label{c21} \\
& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s,\label{c23} \\
& \sum_{f=1}^{F_s}\Omega_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                      
 && \quad \forall f, \forall s  \label{c22}

@@

Equation \eqref{c11}, \eqref{c12} indicates respectively that the power of each RRH do not exceed the maximum power and power of each UE is a positive integer value. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} depicts respectively that the capacity of fronthaul link is limited and the delay of receiving signal should be less than a threshold.  
Furthermore, \eqref{c21}
ensure that each service is mapped to one or more slice.
Also, \eqref{c23} guarantee that each slice (VNFs in two layers of slice) has been placed to one or more physical resources (DC). Moreover, in \eqref{c22}  $\mathfrak{z}\in \{M,R,C\}$, which supports 
that we have enough physical resource for VNFs of each slice.\newline 

@@

&\mathcal{R}_{u_{(v,k)}} \geq  \mathcal{R}_{u_{(v,k)}}^{min} && \quad \forall v, \forall k, \\                                 

@@

\subsection{Proposed Method For Problem \eqref{constraints1}}

@@

We want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.
two different part that can be solved iteratively.  

@@

Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration. Two different method is applied to acquire $\boldsymbol{A}$. The first method is using MOSEK and second method is a heuristic algorithm.

@@

\State Sort services according to their priority, the number of UEs in it and their requirements in descending order.
\State Sort slices according to the number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in descending order. 
\For {$ 1\leq i \leq  S$}
\For {$ 1\leq j \leq  V$}
\State Set $a_{ij} = 1$
\State Obtain Parameters of System
\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} is not applied} 
\State Set $a_{ij} = 0$;

@@

\State break from inner loop;

@@

\subsubsection{Second Sub-Problem}
In this part, by assuming that $\boldsymbol{A}$ is fixed, the optimal power of UEs in each service is achieved.
\begin{theorem}\label{t2}
 $\eta^*$ which is the optimum energy efficiency can be achieved if
\begin{equation}\label{q2}
&\max \limits_{\boldsymbol{P}} (R_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
& R_{total}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
\end{theorem}
Using Lagrangian function and iterative algorithm, can solve this subproblem. 
%\section*{References}
